---
title: "Exhibition of Function Outputs"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r include=FALSE}

# Dataset used in the function
data("iris")

# Package required in the function
library(tidyverse)

# A function enters the iris dataset and a species
# and returns the average sepal length of the selected species.
# The first argument of the function should be the iris dataset.
# The second argument of the function should be 
# one of the species in the iris dataset.
sepal_length_avg <- function(data, species) {
  data_transformed <- data %>%
    filter(Species == species) %>%
    group_by(Species) %>%
    summarise(sepal_length_avg = mean(Sepal.Length))
  return(data_transformed)
}

```

This document exhibits the outputs when specifying different species as the second argument in the function. The function only returns the average sepal length of the selected species.

## The output when specify "virginica" as the second argument
```{r }
sepal_length_avg(iris, "virginica")

```

## The output when specify "setosa" as the second argument
```{r }
sepal_length_avg(iris, "setosa")

```

## The output when specify "versicolor" as the second argument
```{r }
sepal_length_avg(iris, "versicolor")

```


## Appendix: All code in this exercise
```{r,warning=FALSE,message=FALSE,echo=TRUE,results='hide'}
knitr::opts_chunk$set(echo = FALSE)

# Dataset used in the function
data("iris")

# Package required in the function
library(tidyverse)

# A function enters the iris dataset and a species
# and returns the average sepal length of the selected species.
# The first argument of the function should be the iris dataset.
# The second argument of the function should be 
# one of the species in the iris dataset.
sepal_length_avg <- function(data, species) {
  data_transformed <- data %>%
    filter(Species == species) %>%
    group_by(Species) %>%
    summarise(sepal_length_avg = mean(Sepal.Length))
  return(data_transformed)
}

sepal_length_avg(iris, "virginica")

sepal_length_avg(iris, "setosa")

sepal_length_avg(iris, "versicolor")
```
